BlueTracer: \\ a Robust API Tracer for Evasive Malware

### 2018-07-13 Msc-Slides/main.tex
Slides50%

		    \begin{beamerboxesrounded}[shadow=true]{API Hooking}
    The interception of function calls provided by dynamically
linked \\ libraries (DLLs)
    \end{beamerboxesrounded}
    \bigskip

@@

\begin{frame}
	Thanks for the attention.
\end{frame}

>>>>

		    \begin{beamerboxesrounded}[shadow=true]{Evasive malware}
Malware that conceals its harmful behaviour when detecting a
hostile environment, such as a well-known sandbox
solution
    \end{beamerboxesrounded}
    \bigskip

    \begin{figure}
    	\vspace{-0.2cm}
    	\hspace*{1cm}
        \includegraphics[width=9cm]{image/evasive.pdf}
    \end{figure}

    \textbf{Problem 2}: API hooking techniques in literature are not coupled with mechanisms to hide their presence from evasive malware

@@

\begin{frame}
\begin{center}
{\fontsize{15}{15}\selectfont \textbf{Thank you for your attention!}}
\end{center}
\end{frame}
